---
title: "SSXXCoding"
author: "MNHorger"
date: "3/7/2022"
output: html_document
---

#Sleep States Automated Coding 


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(dplyr)
library(ggplot2)
library(lubridate)
library(hms)
library(rmcorr)
library(haven)
library(BlandAltmanLeh)
library(pwr)
library(readxl)
library(magicfor)

```





###Inputting your data 

Change your working directory. 
Read in the data file. Replace all "XX" with the subject number.

```{r}
SSXX <- read_excel("SSXX.xlsx")
```

###Breaking your data into each night, cleaning, and looking for missing data 

Look through the file in excel. Make a note of the start and end row for each night. These will correspond to your Down column. 
  - The Down interval is manually set when coding actigraphy. It 
    encompasses the entire sleep period, even if the infant wakes and/or is
    removed from the bed. 
Current values are only an example

```{r}


SSXXN1 <- SS9['starting row':'ending row',]
night <-c(rep(1, nrow(SSXXN1)))
SSXXN1 <- data.frame(SSXXN1, night)

SSXXN2 <- SSXX[2120:2660, ]
night <-c(rep(1, nrow(SSXXN2)))
SSXXN2 <- data.frame(SSXXN2, night)

SSXXN3 <- SSXX [3570:4116, ]
night <-c(rep(1, nrow(SSXXN3)))
SSXXN3 <- data.frame(SSXXN3, night)

SSXXN4 <- SSXX[5011:5579, ]
night <-c(rep(1, nrow(SSXXN4)))
SSXXN4 <- data.frame(SSXXN4, night)

SSXXN5 <- SSXX[6419:7013, ]
night <-c(rep(5, nrow(SSXXN5)))
SSXXN5 <- data.frame(SSXXN5, night)





#check for missing data 

table(is.na (SSXXN1$`Lifetouch Heart Rate`))
table(is.na (SSXXN2$`Lifetouch Heart Rate`))
table(is.na (SSXXN3$`Lifetouch Heart Rate`))
table(is.na (SSXXN4$`Lifetouch Heart Rate`))
table(is.na (SSXXN5$`Lifetouch Heart Rate`))

table(is.na (SSXXN1$`Lifetouch Respiration Rate`))
table(is.na (SSXXN2$`Lifetouch Respiration Rate`))
table(is.na (SSXXN3$`Lifetouch Respiration Rate`))
table(is.na (SSXXN4$`Lifetouch Respiration Rate`))
table(is.na (SSXXN5$`Lifetouch Respiration Rate`))


```



###Calculate z scores 

```{r}
SSXXN1HRz <- ( SSXXN1$`Lifetouch Heart Rate` - (mean(SSXXN1$`Lifetouch Heart Rate`, na.rm = TRUE))) / sd(SSXXN1$`Lifetouch Heart Rate`, na.rm = TRUE)
SSXXN2HRz <- ( SSXXN2$`Lifetouch Heart Rate` - (mean(SSXXN2$`Lifetouch Heart Rate`, na.rm = TRUE))) / sd(SSXXN2$`Lifetouch Heart Rate`, na.rm = TRUE)
SSXXN3HRz <- ( SSXXN3$`Lifetouch Heart Rate` - (mean(SSXXN3$`Lifetouch Heart Rate`, na.rm = TRUE))) / sd(SSXXN3$`Lifetouch Heart Rate`, na.rm = TRUE)
SSXXN4HRz <- ( SSXXN4$`Lifetouch Heart Rate` - (mean(SSXXN4$`Lifetouch Heart Rate`, na.rm = TRUE))) / sd(SSXXN4$`Lifetouch Heart Rate`, na.rm = TRUE)
SSXXN5HRz <- ( SSXXN5$`Lifetouch Heart Rate` - (mean(SSXXN5$`Lifetouch Heart Rate`, na.rm = TRUE))) / sd(SSXXN5$`Lifetouch Heart Rate`, na.rm = TRUE)




SSXXN1RRz <- ( SSXXN1$`Lifetouch Respiration Rate` - (mean(SSXXN1$`Lifetouch Respiration Rate`, na.rm = TRUE))) / sd(SSXXN1$`Lifetouch Respiration Rate`, na.rm = TRUE)
SSXXN2RRz <- ( SSXXN2$`Lifetouch Respiration Rate` - (mean(SSXXN2$`Lifetouch Respiration Rate`, na.rm = TRUE))) / sd(SSXXN2$`Lifetouch Respiration Rate`, na.rm = TRUE)
SSXXN3RRz <- ( SSXXN3$`Lifetouch Respiration Rate` - (mean(SSXXN3$`Lifetouch Respiration Rate`, na.rm = TRUE))) / sd(SSXXN3$`Lifetouch Respiration Rate`, na.rm = TRUE)
SSXXN4RRz <- ( SSXXN4$`Lifetouch Respiration Rate` - (mean(SSXXN4$`Lifetouch Respiration Rate`, na.rm = TRUE))) / sd(SSXXN4$`Lifetouch Respiration Rate`, na.rm = TRUE)
SSXXN5RRz <- ( SSXXN5$`Lifetouch Respiration Rate` - (mean(SSXXN5$`Lifetouch Respiration Rate`, na.rm = TRUE))) / sd(SSXXN5$`Lifetouch Respiration Rate`, na.rm = TRUE)



#Replace missing data with the mean 
SSXXN1$SSXXN1HRz [is.na(SSXXN1$SSXXN1HRz)] <- 0
SSXXN2$SSXXN2HRz [is.na(SSXXN2$SSXXN2HRz)] <- 0
SSXXN3$SSXXN3HRz [is.na(SSXXN3$SSXXN3HRz)] <- 0
SSXXN4$SSXXN4HRz [is.na(SSXXN4$SSXXN4HRz)] <- 0
SSXXN5$SSXXN5HRz [is.na(SSXXN5$SSXXN5HRz)] <- 0

SSXXN1$SSXXN1RRz [is.na(SSXXN1$SSXXN1RRz)] <- 0
SSXXN2$SSXXN2RRz [is.na(SSXXN2$SSXXN2RRz)] <- 0
SSXXN3$SSXXN3RRz [is.na(SSXXN3$SSXXN3RRz)] <- 0
SSXXN4$SSXXN4RRz [is.na(SSXXN4$SSXXN4RRz)] <- 0
SSXXN5$SSXXN5RRz [is.na(SSXXN5$SSXXN5RRz)] <- 0




#add to the dataset 
SSXXN1 <- data.frame(SSXXN1, SSXXN1HRz, SSXXN1RRz)
SSXXN2 <- data.frame(SSXXN2, SSXXN2HRz, SSXXN2RRz)
SSXXN3 <- data.frame(SSXXN3, SSXXN3HRz, SSXXN3RRz)
SSXXN4 <- data.frame(SSXXN4, SSXXN4HRz, SSXXN4RRz)
SSXXN5 <- data.frame(SSXXN5, SSXXN5HRz, SSXXN5RRz)


```





###Compare each minute to the z score threshold

#### z > .5

```{r}


SSXXN1 <- SSXXN1 %>% 
  mutate(HR50 = case_when(SSXXN1HRz > 0.5 ~ 2, 
                         SSXXN1HRz <= 0.5 ~ 1 ), 
          RR50 = case_when(SSXXN1RRz > 0.5 ~ 2, 
                          SSXXN1RRz <= 0.5 ~ 1)) %>% 
  mutate(Agree = HR50 + RR50, EvalActi50 = Agree*Sleep)

SSXXN2 <- SSXXN2 %>% 
  mutate(HR50 = case_when(SSXXN2HRz > 0.5 ~ 2, 
                         SSXXN2HRz <= 0.5 ~ 1 ), 
          RR50 = case_when(SSXXN2RRz > 0.5 ~ 2, 
                          SSXXN2RRz <= 0.5 ~ 1)) %>% 
  mutate(Agree = HR50 + RR50, EvalActi50 = Agree*Sleep)

SSXXN3 <- SSXXN3 %>% 
  mutate(HR50 = case_when(SSXXN3HRz > 0.5 ~ 2, 
                         SSXXN3HRz <= 0.5 ~ 1 ), 
          RR50 = case_when(SSXXN3RRz > 0.5 ~ 2, 
                          SSXXN3RRz <= 0.5 ~ 1)) %>% 
  mutate(Agree = HR50 + RR50, EvalActi50 = Agree*Sleep)

SSXXN4 <- SSXXN4 %>% 
  mutate(HR50 = case_when(SSXXN4HRz > 0.5 ~ 2, 
                         SSXXN4HRz <= 0.5 ~ 1 ), 
          RR50 = case_when(SSXXN4RRz > 0.5 ~ 2, 
                          SSXXN4RRz <= 0.5 ~ 1)) %>% 
  mutate(Agree = HR50 + RR50, EvalActi50 = Agree*Sleep)

SSXXN5 <- SSXXN5 %>% 
  mutate(HR50 = case_when(SSXXN5HRz > 0.5 ~ 2, 
                         SSXXN5HRz <= 0.5 ~ 1 ), 
          RR50 = case_when(SSXXN5RRz > 0.5 ~ 2, 
                          SSXXN5RRz <= 0.5 ~ 1)) %>% 
  mutate(Agree = HR50 + RR50, EvalActi50 = Agree*Sleep)

```


#### z > 0.25

```{r}

SSXXN1 <- SSXXN1 %>% 
  mutate(HR25 = case_when(SSXXN1HRz > 0.25 ~ 2, 
                         SSXXN1HRz <= 0.25 ~ 1 ), 
          RR25 = case_when(SSXXN1RRz > 0.25 ~ 2, 
                          SSXXN1RRz <= 0.25 ~ 1)) %>% 
  mutate(Agree = HR25 + RR25, EvalActi25 = Agree*Sleep)

SSXXN2 <- SSXXN2 %>% 
  mutate(HR25 = case_when(SSXXN2HRz > 0.25 ~ 2, 
                         SSXXN2HRz <= 0.25 ~ 1 ), 
          RR25 = case_when(SSXXN2RRz > 0.25 ~ 2, 
                          SSXXN2RRz <= 0.25 ~ 1)) %>% 
  mutate(Agree = HR25 + RR25, EvalActi25 = Agree*Sleep)

SSXXN3 <- SSXXN3 %>% 
  mutate(HR25 = case_when(SSXXN3HRz > 0.25 ~ 2, 
                         SSXXN3HRz <= 0.25 ~ 1 ), 
          RR25 = case_when(SSXXN3RRz > 0.25 ~ 2, 
                          SSXXN3RRz <= 0.25 ~ 1)) %>% 
  mutate(Agree = HR25 + RR25, EvalActi25 = Agree*Sleep)

SSXXN4 <- SSXXN4 %>% 
  mutate(HR25 = case_when(SSXXN4HRz > 0.25 ~ 2, 
                         SSXXN4HRz <= 0.25 ~ 1 ), 
          RR25 = case_when(SSXXN4RRz > 0.25 ~ 2, 
                          SSXXN4RRz <= 0.25 ~ 1)) %>% 
  mutate(Agree = HR25 + RR25, EvalActi25 = Agree*Sleep)

SSXXN5 <- SSXXN5 %>% 
  mutate(HR25 = case_when(SSXXN5HRz > 0.25 ~ 2, 
                         SSXXN5HRz <= 0.25 ~ 1 ), 
          RR25 = case_when(SSXXN5RRz > 0.25 ~ 2, 
                          SSXXN5RRz <= 0.25 ~ 1)) %>% 
  mutate(Agree = HR25 + RR25, EvalActi25 = Agree*Sleep)

```


#### z > 0

```{r}

SSXXN1 <- SSXXN1 %>% 
  mutate(HR00 = case_when(SSXXN1HRz > 0 ~ 2, 
                         SSXXN1HRz <= 0 ~ 1 ), 
          RR00 = case_when(SSXXN1RRz > 0 ~ 2, 
                          SSXXN1RRz <= 0 ~ 1)) %>% 
  mutate(Agree = HR00 + RR00, EvalActi00 = Agree*Sleep)

SSXXN2 <- SSXXN2 %>% 
  mutate(HR00 = case_when(SSXXN2HRz > 0 ~ 2, 
                         SSXXN2HRz <= 0 ~ 1 ), 
          RR00 = case_when(SSXXN2RRz > 0 ~ 2, 
                          SSXXN2RRz <= 0 ~ 1)) %>% 
  mutate(Agree = HR00 + RR00, EvalActi00 = Agree*Sleep)

SSXXN3 <- SSXXN3 %>% 
  mutate(HR00 = case_when(SSXXN3HRz > 0 ~ 2, 
                         SSXXN3HRz <= 0 ~ 1 ), 
          RR00 = case_when(SSXXN3RRz > 0 ~ 2, 
                          SSXXN3RRz <= 0 ~ 1)) %>% 
  mutate(Agree = HR00 + RR00, EvalActi00 = Agree*Sleep)

SSXXN4 <- SSXXN4 %>% 
  mutate(HR00 = case_when(SSXXN4HRz > 0 ~ 2, 
                         SSXXN4HRz <= 0 ~ 1 ), 
          RR00 = case_when(SSXXN4RRz > 0 ~ 2, 
                          SSXXN4RRz <= 0 ~ 1)) %>% 
  mutate(Agree = HR00 + RR00, EvalActi00 = Agree*Sleep)

SSXXN5 <- SSXXN5 %>% 
  mutate(HR00 = case_when(SSXXN5HRz > 0 ~ 2, 
                         SSXXN5HRz <= 0 ~ 1 ), 
          RR00 = case_when(SSXXN5RRz > 0 ~ 2, 
                          SSXXN5RRz <= 0 ~ 1)) %>% 
  mutate(Agree = HR00 + RR00, EvalActi00 = Agree*Sleep)

```






